\chapter{Glossary}
\paragraph{\Compose*[Java]} Compose*.Java is the Java port of Compose*.
\paragraph{\Compose*[DotNET]} Compose*.Net is the .Net port of Compose*.
\paragraph{\Compose*{} developer} A member of the Compose* team, thus who programs on Compose*.
This term is used to avoid the ambiguous term Compose* programmer.
\paragraph{\Compose*{} user} Somebody who uses Compose*, this does not exclude the
person from being a Compose* developer. This term is used to avoid the ambiguous term Compose* programmer.
\paragraph{Default constructor} A constructor without any argument.

\paragraph{Functional complete} A set of logical operators is functional complete when it can express any operator from
the set~\cite{vanBenthem91}.
So a XOR (exclusive OR) is not in a functional complete set, because 
$A~XOR~B~=~(A~AND~!B)~OR~(!A~AND~B)$. The smallest
functional complete set only contains OR and NOT.

\paragraph{Language independence} Compose* is designed to be used for any language, that gives that Compose*
needs to be language independent. This language in dependency influences Compose* in two ways, first on the
syntax and semantics, and second on the under laying mechanisms. True language independence means that a concern can be added to
an application to a random parent language and it behaves he same as if you would place it in the same application
written in a different parent language. For the syntax and semantics this means that we cannot add primitive types to
Compose*, because for instance \emph{int}, \emph{char}, and \emph{double}, can have different ranges.
These limitations can be solved by
automating some conversions, for instance we could introduce our own primitive type \emph{i} which is an integer
of 32 bits, then we can transform this primitive to the primitive value we want by creating a conversion method in
Compose*. However for every work around in the language applies that it is just more code and even more important
that it solves the problem for most of the cases, but is would cause errors in a small number of situations.
For instance we go further with our primitive i, we find ourselves in the situation that this idea only works if the
application stays on one platform and one parent language, if we would import a library then we cannot say for certain
to what primitive type we must convert. So if we apply the our own defined primitives we limit the use of the parent language,
which is something we do not want.

This gives that there are a few basic comments on language independence which are common for all the parts of the
Compose* language:

\begin{itemize}[noitemsep]
\item Keywords from parent languages have language specific meanings, that means that we cannot use them
directly in Compose*.
\item The things that are language independent are Objects, Methods, Packages, and Annotations. However these
might not be available in every language, for instance C does not know Objects and Annotations are not common for all
languages.
\item Workarounds with conversion mechanisms might work, but probably it conceptual not sound or you limit
yourself in another way.
\item If something, for example an integer is 32 bit, in most languages, say Java, C\#, C++, Delphi, then it dos not mean
that it can be made language independence. There is probably one language around where the integer is not 32 bit.
\end{itemize}

\paragraph{Signature of a class} There are various definitions of the signature of a class, the one used in \Compose* is
that the signature of a class is the collection of signatures of the methods of the class. The signature of a class
is the name, return type, and the list of parameter types. The signature of the class in \autoref{glos::signature}
is \{\emph{Sting getName, void setBirthDate(Date), void setBirthDate(String)} \}.

\begin{lstlisting}[caption={Example class in Java},label=glos::signature,float=h,language=Java,style=listing]
public class Person{
	public String getName(){}
	public void setBirthDate(Date date){}
	public void setBirthDate(String date){}
}
\end{lstlisting}

\paragraph{Base language} \Compose* is an extension to other programming languages, the base language is the language
that gets extended. So for \Compose*[Java] the programming language Java is the parent language.

\paragraph{Wild card} The used term for the `*' token, whereas it normally means everything, it means in \Compose*
ignore.